---
title: "muxViz"
author: Alexis Hucteau
date: "`r Sys.Date()`"
output:
    html_document:
      toc: yes
      toc_float: yes
      theme: united
editor_options:
  markdown:
    wrap: sentence
---

```{r}
rm(list = ls())
suppressPackageStartupMessages({
  library(dplyr)
  library(RCy3)
  library(igraph)
  library(data.table)
  library(stringr)
  library(clusterProfiler)
  library(ggplot2)
  library(muxViz)
  library(grid)
  library(ggraph)
})

"%ni%" <- Negate("%in%")
```

Preparing the data

The preparation of input files is very easy. MuxViz requires plain text ASCII files to work, with columns separated by some special character (e.g. backspace, “,”, “;”, etc). At least three files are required:

    A configuration file, where path(s) to network(s) data are specified;
    A layout file, where information about nodes is specified;
    An edge-list file, where edges are specified (for edge-colored networks, one file is needed for each layer; for interconnected networks an extended edge-list format can be used)

```{r}
All_samples_network <- read.table("Results/GRN/Network_for_muxviz.tsv", sep = "\t", header = T)
```

